### 2023-05-24 application.tex
up

\begin{proposition}
{\sc Bounded-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is in $\EXPSPACE$.
\end{proposition}

>>>>

\begin{proposition}
{\sc Bounded-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is decidable.
\end{proposition}
\mathieu{Besoin de vérifier la complexité détaillée}
